---
title: Functional Rarity Indices are affected by the number and nature of the used
  traits
author: "Matthias Grenié"
date: "23 avril 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim to be a brain dump to test a number of hypotheses on the variation of functional rarity indices depending on the nature and number of the traits involved.

ideas:

* Change number of traits and look at the differences of distinctiveness considered
* Change nature of traits (quantitative continuous, semi-quantitative, nominal)
* Explore relation between Distinctiveness and Scarcity
* Importance of weighing the different facets when estimating functional rarity
* Simulate real trait evolution/correlation and see influences on considered indices
* Simulations vs. use case to get a grasp of the importances on considering traits


## Simulate species trait

```{r simulate_species}
library("tidyverse")

set.seed(23042018)

n_species = 100  # Number of species to simulate

n_continuous  = 2  # Number of continous trait to simulate
n_ordered     = 4  # Number of ordered traits
n_categorical = 1  # Number of categorical traits

species_traits = data.frame(
    species = paste0("sp_", seq(n_species))
)

trait_continuous = map(seq(n_continuous) %>%
                           set_names(nm = paste0("tr_c_", .)),
                       ~rnorm(n_species)) %>%
    as.data.frame()
rownames(trait_continuous) = species_traits$species

trait_ordered = map(seq(n_continuous) %>%
                           set_names(nm = paste0("tr_o_", .)),
                    ~sample(1:5, n_species, replace = TRUE)) %>%
    as.data.frame()
rownames(trait_ordered) = species_traits$species

trait_categorical = map(seq(n_categorical) %>%
                            set_names(nm = paste0("tr_cat_", .)),
                        ~ sample(letters[1:5], n_species, replace = TRUE)) %>%
    as.data.frame()
rownames(trait_categorical) = species_traits$species


species_traits = cbind(species_traits,
                       trait_continuous,
                       trait_ordered,
                       trait_categorical)
```

```{r func_dist}
# Compute functional distnaces

library("ade4")

ktab_list = ktab.list.df(list(trait_continuous,
                              trait_ordered,
                              trait_categorical))

ktab_cor = kdist.cor(ktab_list, c("Q", "O", "N"), option = c("scaledBYrange"))
```





